{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-14 brains-protocol.tex
Merge

\subsection{Alteration}

Next, we measure how a word $\wstart$'s feature varies as $\wstart$ is substituted by $\warrival$, i.e. $\phi(\warrival) - \phi(\wstart)$.
Averaging this value over all start words such that $\phi(w) = f$ yields the mean variation for that feature value~$f$:
$$\Delta_{\phi}(f) = \left< \phi(\warrival) - \phi(\wstart) \right>_{\left\lbrace (\wstart,\warrival) | \phi(\wstart) = f \right\rbrace}$$

We introduce a null hypothesis $\mathcal{H}_0$ to compare the actual variation of a word's feature to its expected variation, assuming the arrival word $\warrival_0$ had been chosen randomly from the pool of free association words.
The new quantity under $\mathcal{H}_0$ is:
\footnote{Note that $\phi(\warrival_0)$ is in fact a constant in this averaging, since by definition $\warrival_0$ does not depend on $\wstart$.}
$$\Delta_{\phi}^0 (f) = \left< \phi({\warrival_0}) - \phi(\wstart) \right>_{\left\lbrace (\wstart,\warrival_0) | \phi(\wstart) = f \right\rbrace}$$

We also considered an alternative null hypothesis, denoted $\mathcal{H}_{00}$, where the arrival word is chosen randomly \emph{among immediate synonyms of the start word}, i.e. an arrival word chosen among semantically plausible though still random words.\footnote{In this case $\warrival_{00}$ does depend on $\wstart$.}
The results were not qualitatively changed with this second null hypothesis, so for the sake of clarity we chose to present the results using the simpler~$\mathcal{H}_0$.

Using this method we obtain the mean variation of feature for each start feature value, and can compare the variations to a situation where arrival words are chosen randomly.
This gives us a fine-grained view of how word features evolve upon substitution.

>>>>

\subsection{Variation}

Next, we measure how a word $\wstart$'s feature varies as $\wstart$ is substituted by $\warrival$, i.e. $\phi(\warrival) - \phi(\wstart)$.
Averaging this value over all start words such that $\phi(w) = f$ yields the mean variation for that feature value~$f$:
$$\Delta_{\phi}(f) = \left< \phi(\warrival) - \phi(\wstart) \right>_{\left\lbrace \wstart\rightarrow\warrival | \phi(\wstart) = f \right\rbrace}$$

We introduce a null hypothesis $\mathcal{H}_0$ to compare the actual variation of a word's feature to its expected variation, assuming the arrival word $\warrival$ has been chosen randomly from the pool of free association words.
In this case, since $\phi(\warrival)$ becomes a constant value in the above averaging (by definition $\warrival$ does not depend on $\wstart$ anymore) and $\phi(\wstart)=f$,  the baseline variation under $\mathcal{H}_0$ may be rewritten as:
$$\Delta_{\phi}^0 (f) = \left<\phi\right>-f$$

We also considered an alternative null hypothesis, denoted $\mathcal{H}_{00}$, where the arrival word is randomly chosen \emph{among immediate synonyms of the start word}, \hbox{i.e.} an arrival word chosen among semantically plausible though still random words.\footnote{In this case $\warrival_{00}$ does depend on $\wstart$.}
The results were not qualitatively different under this second null hypothesis, so for the sake of clarity we chose to keep the simpler~$\mathcal{H}_0$.

Using this method we obtain the mean variation of feature for each start feature value, comparing the variations to a situation where arrival words are chosen randomly.  This gives us a fine-grained view of how word features evolve upon substitution.
